---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# The UnitCircle Package

As of now this package only containts the `uc.check` function wich checks whether the roots of a given polynomial lie outside the Unit circle.

# Usage

The function `uc.check` has the following Arguments:

Argument | Description
------------- | --------------------------------------------------------------------
pol_  | A vector of polynomial coefficients in increasing order.
plot_output  | Logical that defines whether a graphical output should be created.
print_output  | Logical that defines whether to print the results.


# Examples:

```{r}
library(UnitCircle)
uc.check(pol_ = c(1,0,0.99999), plot_output = FALSE)
```

```{r}
uc.check(pol_ = c(2,0,2.2,-3), plot_output = TRUE)
```

## Installation

### Install from CRAN

I'm sorry but installing UnitCircle from CRAN isn't possible atm.

### Install the latest development version

You can install the latest development version from github with

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("BerriJ/UnitCircle")
```

## License

* **UnitCircle** is licensed under [GPL-3](LICENSE)
